---
title: "DNA Alignments"
author: "RicardoQi"
date: '2022-03-03'
output: html_document
---
Packages are installed.
```{r}
r = getOption("repos")
r["CRAN"] = "http://cran.us.r-project.org"
options(repos = r)
install.packages("BiocManager")

install.packages("genbankr")
install.packages("Biostrings")
install.packages("ggtree")
install.packages("annotate", force= TRUE)
install.packages("muscle")

install.packages("reshape2")
install.packages("rentrez")
```
Packages are loaded before using.
```{r}
library(rentrez)
library(genbankr)
library(annotate)
library(ape)
```
The ID of the gene is entered to be read in the code.
```{r}
BbID<-GBAccession("NC_045512.2")
BbGbk<-readGenBank(BbID)
```
Use class() to return the class of the gene.
```{r}
class(BbGbk)
```
Then the coding sequence is shown.
```{r}
cds(BbGbk)
```
RNA sequences that are transcribed from DNA are presented.
```{r}
transcripts(BbGbk)
```
Exons are interpreted.
```{r}
exons(BbGbk)
```
a list of sequences corresponding to genes is returned using gene().
```{r}
genes(BbGbk)
```
Other features are provided.
```{r}
otherFeatures(BbGbk)
```
Then str() is used to help understand the structure.
```{r}
str(BbGbk)
```
According to the string inforamtion, we can determine that the gene is originated from human, and it is a genome named Severe acute respiratory syndrome coronavirus. 
```{r}
BbTree<-nj(BbGbk)
ggtree(BbTree)
```